Forcing for Isabelle

### 2018-12-21 LICS/easy-axioms.tex
Mencionando dot G y explicitando la dificultad de tener check_in_M

The proof of Infinity for $M[G]$ takes advantage of some absoluteness
results proved in the locale \isa{M{\isacharunderscore}trivial}; this
proof is easy because we assume $\chk(x) \in M$ whenever $x\in
M$. Since we have already proved that $M[G]$ is transitive,
$\emptyset\in M[G]$ assuming $G$ being generic, and also that it
satisfies Pairing and Union, we can instantiate
\isa{M{\isacharunderscore}trivial}:
\begin{isabelle}
\isacommand{sublocale}\isamarkupfalse%
\ G{\isacharunderscore}generic\ {\isasymsubseteq}\ M{\isacharunderscore}trivial{\isachardoublequoteopen}{\isacharhash}{\isacharhash}M{\isacharbrackleft}G{\isacharbrackright}{\isachardoublequoteclose}
\end{isabelle}
We assume that $M$ satisfies Infinity, i.e., that Infinity relativized
to $M$ holds; therefore we obtain $I \in M$ such that $\emptyset\in I$
and, $x \in I$ implies $\mathit{succ}(x)\in I$ by absoluteness of
empty and successor for $M$. Using the assumption that $M$ is closed
under $\chk$, we deduce $\val(G,\chk(I)) = I \in M[G]$.  Now we can
use absoluteness of emptyness and successor, this time for $M[G]$, to
conclude that $M[G]$ satisfies Infinity.
% \begin{isabelle}
%   \isacommand{lemma}\isamarkupfalse%
% \ infinty{\isacharunderscore}in{\isacharunderscore}MG\ {\isacharcolon}\ {\isachardoublequoteopen}infinity{\isacharunderscore}ax{\isacharparenleft}{\isacharhash}{\isacharhash}M{\isacharbrackleft}G{\isacharbrackright}{\isacharparenright}{\isachardoublequoteclose}
% \end{isabelle}

>>>>

The proof of Infinity for $M[G]$ takes advantage of some absoluteness
results proved in the locale \isa{M{\isacharunderscore}trivial}; this
proof is easy because we work in the context of the locale
\isa{M{\isacharunderscore}extra{\isacharunderscore}assms} which states
the assumption $\chk(x) \in M$ whenever $x\in M$. Since we have
already proved that $M[G]$ is transitive, $\emptyset\in M[G]$ assuming
$G$ being generic, and also that it satisfies Pairing and Union, we
can instantiate \isa{M{\isacharunderscore}trivial}:
\begin{isabelle}
\isacommand{sublocale}\isamarkupfalse%
\ G{\isacharunderscore}generic\ {\isasymsubseteq}\ M{\isacharunderscore}trivial{\isachardoublequoteopen}{\isacharhash}{\isacharhash}M{\isacharbrackleft}G{\isacharbrackright}{\isachardoublequoteclose}
\end{isabelle}
We assume that $M$ satisfies Infinity, i.e., that Infinity relativized
to $M$ holds; therefore we obtain $I \in M$ such that $\emptyset\in I$
and, $x \in I$ implies $\mathit{succ}(x)\in I$ by absoluteness of
empty and successor for $M$. Using the assumption that $M$ is closed
under $\chk$, we deduce $\val(G,\chk(I)) = I \in M[G]$.  Now we can
use absoluteness of emptyness and successor, this time for $M[G]$, to
conclude that $M[G]$ satisfies Infinity.
% \begin{isabelle}
%   \isacommand{lemma}\isamarkupfalse%
% \ infinty{\isacharunderscore}in{\isacharunderscore}MG\ {\isacharcolon}\ {\isachardoublequoteopen}infinity{\isacharunderscore}ax{\isacharparenleft}{\isacharhash}{\isacharhash}M{\isacharbrackleft}G{\isacharbrackright}{\isacharparenright}{\isachardoublequoteclose}
% \end{isabelle}

### 2018-12-21 LICS/recursion.tex
Mencionando dot G y explicitando la dificultad de tener check_in_M

We close our discussion of names and their values by making explicit
the names for elements in $M$, once more we refer to
\cite{2018arXiv180705174G} for our formalization. The definition of
$\chk(x)$ is a straightforward $\in$-recursion:
\begin{equation*}
  \label{eq:def-check}
  \chk(x)\defi\{\lb\chk(y),\1\rb : y\in x\}
\end{equation*}
It can be easily proved by $\in$-induction that $\val(G,\chk(x))=x$.
To conclude $M\subseteq M[G]$ one also needs to have $\chk(x) \in M$;
this result requires the internalization of recursively defined
functions. We indicate explicitly where we use this assumption.

>>>>

We close our discussion of names and their values by making explicit
the names for elements in $M$, once more we refer to
\cite{2018arXiv180705174G} for our formalization. The definition of
$\chk(x)$ is a straightforward $\in$-recursion:
\begin{equation*}
  \label{eq:def-check}
  \chk(x)\defi\{\lb\chk(y),\1\rb : y\in x\}
\end{equation*}
It can be easily proved by $\in$-induction that $\val(G,\chk(x))=x$.
But to conclude $M\subseteq M[G]$ one also needs to have
$\chk(x) \in M$; this result requires the internalization of
recursively defined functions. This is also needd to prove
$G \in M[G]$; let us define
$\dot G= \{\lb \chk(p),p\rb : p \in \PP \}$, it is easy to prove
$\val(G,\dot G) = G$. Proving $\dot G\in M$ involves
knowing $\chk(x) \in M$ and using one instance of Replacement.

Paulson proved absoluteness results for definitions by recursion and
one of our next goals is to instantiate the appropiate locale
\isa{M{\isacharunderscore}eclose} which is the last layer of a pile of
locales; it will take us some time to prove that any ctm satisfies the
assumptions involved in those locales. In the meantime, we declare a
locale \isa{M{\isacharunderscore}extra{\isacharunderscore}assms}
assembling both assumptions.
